\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}

\pagestyle{headings}

\title{Buddha Import}
\author{An introduction to the Asian engineers importation}
\date{December 2011}

\begin{document}

\maketitle 

\paragraph{What are we doing}
Our company have been specialised in the importation of Asians software
engineers for more than ten years. Our imported engineers are able to complete
complex tasks, like building amazing Java management applications from scratch,
with less than the fourth of the price of an European engineer.

We don't know why they are called "engineer" because you don't need to be an engineer to develop 
Java applications but they are not well paid so it is not a problem for us to call them engineers !


\paragraph{Personal details}
We are 3 employees from our Ukrainian offices, near Prypiat. All of us are
working on the seeking of new clients.


\paragraph{Personnel}
In ten years, our company have grown to around one hundred workers. We have
plans to provide temporary workers to increase our benefits.

They are very temporary because of the irradiations which make them very pale after a few weeks among us.

\paragraph{Products and services}
We offer a large range of competences, from Java computer scientist to Oracle
administrator.  People like that need to be restricted in a Zone.

We are in contact with top Indian and Chinese universities. Our
new temporary workers service will be able to give working force to our
customers without the price of a full time employment. 

\paragraph{Market}
Buddha Import is the largest European company specialised in engineers
importation and our prices are the lowest of this market.

\paragraph{Marketing}
We have a lot of consultants to help our clients to find exactly what they
need. We are able to give precise estimations of costs reduction to our
customers, which is a huge advantage in customers relations.

\paragraph{Premises and logistics}
Buddha Import is located in Ukraine. We have our own planes for the importation
and we plan to buy two new Airbus A380, so we will be able to import four
hundreds engineers per day.


\end{document}